Interspecies comparisons of Mg/Ca ratios in limpet shells

### 2024-06-23 Manuscript.tex
added citation

The analysed specimens, their origin and studies with background
information can be found in Table 1.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}@{}}
\caption{Table 1 Overview of the modern and archaeological limpet
specimens analysed in this study \{\#tab:specimens\}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Context
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Study
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Species
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Location
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Sample ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Previous analyses
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Context
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Study
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Species
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Location
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Sample ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Previous analyses
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Modern & \citep{Nicastro2020-ih} & \emph{N. deaureata} & Bahía
Cambaceres Exterior - Tierra del Fuego (AR) & ND-1016-3 & Stable oxygen
and carbon isotope analysis \\
& & & & ND-1016-4 & \\
& & \emph{N. magellanica} & & NM-1016-1 & \\
& & & & NM-1016-3 & \\
& \citep{Graniero2017-io} & \emph{P. vulgata} & Rack Wick Bay - Westray
(UK) & ORK-LT5 & Stable oxygen and carbon isotope analysis; Mg, Li, Sr,
Ca,. \\
Archaeological & \citep{Surge2012-ba} & \emph{P. vulgata} & Rack Wick
Bay - Westray (UK) & QG1-7188-1 & Stable oxygen and carbon isotope
analysis \\
& & & & QG1-7189-2 & \\
& & & & QG2-1061-1 & \\
& & & & QG2-1064-1 & \\
& & & & QG2-7180-1 & \\
& & & & QG2-7180-2 & \\
& & & & QG1-7246-1 & \\
& This study & \emph{N. magellanica} & Heshkaia 35 & Heshkaia\_35-1 &
\emph{none} \\
& & \emph{N. deaureata} & & Heshkaia\_35-2 & \\
& & \emph{N. deaureata} & & Heshkaia\_35-3 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-4 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-5 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-6 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-7 & \\
& & \emph{N. deaureata} & & Heshkaia\_35-8 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-9 & \\
\end{longtable}

>>>>

The analysed specimens, their origin and respective studies with
research background information can be found in Table 1. Here we will
briefly summarise their contextual information, which can be accessed in
more detail at the respective studies
\citep{Nicastro2020-ih, Surge2012-ba, Graniero2017-io}. While those
studies also included other specimens, their accessibility or state of
preservation did not all lend them to be re-analysed.

There are two main locations that we sourced specimens from: the island
of West Ray in Orkney (UK) and the Beagle Channel in Tierra del Fuego
(Argentina). A modern shell on West Ray was collected in Rack Wick Bay
in August 2009, which experiences virtually no freshwater input. The
temperature

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}@{}}
\caption{Table 1 Overview of the modern and archaeological limpet
specimens analysed in this study \{\#tab:specimens\}}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Context
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Study
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Species
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Location
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Sample ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Previous analyses
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Context
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Study
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Species
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Location
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Sample ID
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Previous analyses
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Modern & \citep{Nicastro2020-ih} & \emph{N. deaureata} & Cambaceres Bay
- Tierra del Fuego (AR) & ND-1016-3 & Stable oxygen and carbon isotope
analysis \\
& & & & ND-1016-4 & \\
& & \emph{N. magellanica} & & NM-1016-1 & \\
& & & & NM-1016-3 & \\
& \citep{Graniero2017-io} & \emph{P. vulgata} & Rack Wick Bay - Westray
(UK) & ORK-LT5 & Stable oxygen and carbon isotope analysis; Mg, Li, Sr,
Ca,. \\
Archaeological & \citep{Surge2012-ba} & \emph{P. vulgata} & Rack Wick
Bay - Westray (UK) & QG1-7188-1 & Stable oxygen and carbon isotope
analysis \\
& & & & QG1-7189-2 & \\
& & & & QG2-1061-1 & \\
& & & & QG2-1064-1 & \\
& & & & QG2-7180-1 & \\
& & & & QG2-7180-2 & \\
& & & & QG1-7246-1 & \\
& This study & \emph{N. magellanica} & Heshkaia 35 in Moat Bay - Tierra
del Fuego (AR) & Heshkaia\_35-1 & \emph{none} \\
& & \emph{N. deaureata} & & Heshkaia\_35-2 & \\
& & \emph{N. deaureata} & & Heshkaia\_35-3 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-4 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-5 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-6 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-7 & \\
& & \emph{N. deaureata} & & Heshkaia\_35-8 & \\
& & \emph{N. magellanica} & & Heshkaia\_35-9 & \\
\end{longtable}

{\centering \includegraphics{Manuscript_files/figure-pdf/SST Data-1.pdf}

\caption{SST values averaged over the last 20 years. SST values were
sourced from \citep{europeanunion-copernicusmarineservice2015}}
